---
title: "Otter-food-behavior"
output: html_document
---

## What?

Analysis of otter behavior with certain foods in a zoo.
What food do the otters prefer more; trout, mussels, or crab? Do they Share the same food they beg the most for?


# Programs loaded in

```{r, message=FALSE}
library(dplyr)
library(ggplot2)
```

## The original Data 

```{r, cache=TRUE}
otter_data <- read.csv("../data/Bowden-ParryOtterdata.csv")
head(otter_data)
```


## Analysis 1

Singling out the data I need for preferred foods

What food do the otters prefer more; trout, mussels, or crab?
using the columns of data, foodtype, totalbeg and begreceived.
making begreceived to be > 0 to exclude trials that did not receive food when they wanted it.
making the totalbeg > 0 so I could see if the otters wanted that food or not.

Total beg shows if the otters begged for that food
Beg received shows if the Otter received the food they begged for

```{r}
begging <-   
  otter_data %>%
  filter(begreceived > 0, totalbeg > 0) %>% 
  select(foodtype, totalbeg, begreceived)

knitr::kable(head(begging))
```

## Plotting begged v recieved foods

```{r}
ggplot(begging, aes(x = begreceived, y = totalbeg, color = foodtype)) +
  geom_point() +
  geom_jitter(size = 2, width = 1, height = 1)
  
```

```{r}
ggplot(begging, aes(x = begreceived, y = totalbeg)) +
  geom_point(alpha = 0.2) +
  geom_jitter(size = 1, width = 0.7, height = 0.7) +
  facet_wrap(~foodtype)
  
```


```{r}
ggplot(begging, aes(x = totalbeg)) +
  geom_histogram() +
  facet_wrap(~foodtype)
  
```


### what does that mean?

 - mussels
 - crab 
 - trout



## Analysis 2

Singling out data to see if they are sharing the food they are begging for the most

```{r}
sharing <- 
  otter_data %>% 
  filter(begreceived > 0, sharingbybegonly > 0) %>% 
  select(begreceived, sharingbybegonly, foodtype)

knitr::kable(head(sharing))
```


# plotting if the food was shared

```{r}
ggplot(sharing, aes(x = begreceived, y = sharingbybegonly)) +
  geom_point(size = 3, alpha = 0.5) +
  facet_wrap(~foodtype)
  
```



```{r}
ggplot(sharing, aes(x = begreceived, y = sharingbybegonly, color = foodtype)) +
  geom_point() +
  geom_jitter(size = 2, width = 1, height = 1) +
  facet_wrap(~foodtype)
  
```

## What?

Did the otters share the food they begged the most for?
 - yes
 - also shared the food the begged theleast for

