---
title: "Otter-food-behavior"
output: html_document
---

## What?

Analysis of otter behavior with certain foods in a zoo.
What food do the otters prefer more; trout, mussels, or crab? Do they Share the same food they beg the most for?


# chunks

```{r, message=FALSE}
library(dplyr)
library(ggplot2)
```

## Data

```{r, cache=TRUE}
otter_data <- read.csv("../data/Bowden-ParryOtterdata.csv")
head(otter_data)
```


## Analysis

What food do the otters prefer more; trout, mussels, or crab?
using the columns of data, foodtype, totalbeg and begreceived.
making begreceived to be > 0 to exclude trials that did not receive food when they wanted it.
making the totalbeg > 0 so I could see if the otters wanted that food or not.

Total beg shows if the otters begged for that food
Beg received shows if the Otter received the food they begged for

```{r}
begging <-   
  otter_data %>%
  filter(begreceived > 0, totalbeg > 0) %>% 
  select(foodtype, totalbeg, begreceived)

knitr::kable(head(begging))
```

## Plot

```{r}
ggplot(begging, aes(x = begreceived, y = totalbeg)) +
  geom_point(size = 3, alpha = 0.5) +
  facet_wrap(~foodtype)
  
```










